Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-04-10 manuscript/sections/results.tex
Finish section on moving to 2030

\vspace{5pt}
\begin{res}
    24/7 CFE procurement comes with a cost premium. 
    However, the 90\%--95\% CFE targets have only a small cost premium over 100\% annual renewable matching. 
    With solar, wind and batteries, 100\% CFE target comes at much higher costs.
\end{res}

@@

\vspace{10pt}
\begin{res}
    24/7-CFE procurement triggers investment in new technologies the system will need later: long-duration storage and new clean firm generation.
\end{res}

@@

As can be expected, the cleaner grid in the German case results in a lower value of the average emissions rate of participating consumers than in the case of Poland. 
The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}

Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching once CFE target is tight enough. 
As expected at 100\% CFE target, participating consumers achieve a zero emission rate associated to their electricity consumption, since they perfectly match demand and clean generation on hourly basis.

@@

\cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions} show also similar trends to the base scenario. 
For lower CFE targets, participating consumers can complement portfolio with electricity imports from grid. To achieve higher CFE targets, an clean firm generatorion is added to the portfolio, which greatly reduces the need for renewable generation capacity to match load on an hourly basis. 
In the case of Germany and Poland, both the Allam cycle generator with CCS and advanced dispatchable generator enter the optimal procurement strategy. 
This is likely due to a case that these regions are better interconnected with the rest of the European electrcity grid than Ireland. 
A better interconnection makes possible to exhaust all arbitrage opportunities across time and space and maximise the dispatch value from an advanced dispatchable generator with low variable costs.

@@

Note that for lower CFE targets, constraint (2) is not binding, what makes the same cost-optimal shares of procured portfolio and grid imports repeat until the CFE target becomes tight enough.

@@

text

>>>>

\vspace{5pt}
\begin{res}
    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching. 100\% 24/7 CFE can be achieved with solar, wind and battery storage, but at a high cost premium.
\end{res}

@@

\vspace{10pt}
\begin{res}
    24/7 CFE procurement triggers investment in new technologies the system will need later: long-duration storage and advanced clean firm generators.
\end{res}

@@

As can be expected, the cleaner grid in the German case results in a lower value of the average emissions rate of participating consumers than in the case of Poland. 
The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching once CFE target is tight enough. 
As expected at 100\% CFE target, participating consumers achieve a zero emission rate associated to their electricity consumption, since they perfectly match demand and clean generation on hourly basis.

@@

\cref{fig:10-2025-DE-p3-ci_costandrev} and \cref{fig:10-2025-PL-p3-ci_costandrev} also show similar trends to the base scenario. 
For lower CFE targets, participating consumers can complement portfolio with electricity imports from grid. To achieve higher CFE targets, an clean firm generatorion is added to the portfolio, which greatly reduces the need for renewable generation capacity to match load on an hourly basis. 
In the case of Germany and Poland, both the Allam cycle generator with CCS and advanced dispatchable generator enter the optimal procurement strategy. 
This is likely due to a case that these regions are better interconnected with the rest of the European electrcity grid than Ireland. 
A better interconnection makes possible to exhaust all arbitrage opportunities across time and space and maximise the dispatch value from an advanced dispatchable generator with low variable costs.

@@

\vspace{10pt}
\begin{res}
    In 2030, participating consumers benefit from decreasing costs of clean technologies and cleaner state of the electricity grids.
\end{res}

\vspace{5pt}
\begin{res}
    Voluntary commitments to clean electricity procurement bring system value even in
    cleaner grids. Similarly to the base scenario, 24/7 hourly matching results in deeper decarbonisation than 100\% annual renewable matching if CFE targets are above certain treshhold.
\end{res}

In the scenarios above, we have been exploring 24/7 clean electricity procurement within the European electricity system, with a focus on the year 2025. 
In this section, we shift our attention to the results and implications of these procurement strategies for the year 2030. 
This will provide a deeper understanding of the long-term effects and the potential evolution of clean energy procurement across Europe, as companies continue to adapt their procurement strategies to achieve carbon-free energy goals.

From the modelling perspective, many system parameters change with a five year step to 2030. 
In particular, the technology costs decline due to economics of scale and incremental innovation, national energy- and climate policies become more tight, and some legacy power plants leave the market. 
An overarching feature of the five-year step is a cleaner state of the electricity grids.

\cref{fig:10-2030-IE-6plots} illustrates the results for the "base scenario" moved five years into the future to 2030, with all other factors held constant.

\cref{fig:10-2030-IE-p1-used} shows the fraction of hourly demand met with clean electricity for each procurement policy -- now in 2030. 
There two observations from comparing these results with a base scenario.
First, in the reference case, 72\% of demand is met with CFE, which is 18\% more than in 2025, which is a result of a cleaner electricity grid on a background. 
Thus, lower CFE targets (such as 80\%) are met with a larger share of grid imports. 
Second, higher CFE targets still require a independency from grid imports for the perfect match of clean electricity with \gls{ci} load on hourly basis. 
At 100\% 24/7 CFE, participating consumers rely only on procured resources.

The average emissions rate of 24/7 participating consumers is intuitively lower with a cleaner regional network. 
As shown in \cref{fig:10-2030-IE-p1-ci_emisrate}, the reference case value is reduced from 240~g\co/kWh in 2025 to 107~g\co/kWh in 2030.
The dynamics of 24/7 CFE procurement remains also in 2030. An hourly 24/7 matching allows for net-zero emissions associated with the \gls{ci} buyers' consumption, with a lower emission rate than 100\% annual matching already at 90\% CFE target.
An interesting result is that a CFE target of 90\% yields lower \gls{ci} emission rate, although costs the same as the 100\% annual matching for all three technological palettes (see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p1-ci_costandrev}).

\cref{fig:10-2030-IE-p1-zone_emissions} show that both 100\% annual matching with renewable energy and the 24/7 hourly matching with \gls{cfe} keep positive effect on system-level emissions even in cleaner system. 
Similarly to 2025, if CFE target is high enough, a diverse resource portfolio procured by 24/7 participating consumers has a larger impact on net system emissions in a local zone than 100\% annual matching.
Interestingly, in the case of 2030, 100\% 24/7 CFE nearly doubles the decarbonisation effect of 100\% annual matching: 100\% RES reduces emissions in the local zone by 0.2~Mt\co/a (8\% of Irish power section emissions), while 100\% 24/7 CFE yields reduction of 0.4~Mt\co/a. The nature of this effect is explained in \cref{subsec:mechanisms}.

The \gls{ci} cost breakdown for Ireland 2030 scenario shows that net costs for 24/7 CFE matching fall for all technological palettes. Participating consumers benefit from decreasing costs of clean technologies and cleaner state of the electricity grids.
\cref{fig:10-2030-IE-p2-ci_costandrev} and \cref{fig:10-2030-IE-p1-ci_costandrev} show that in 2030, cost-optimal portfolio mix procured by the \gls{ci} participants for CFE 100\% target has a very limited cost premium to 100\% annual renewable matching with LDES and clean firm technologies. 
At the same time, participanting consumers achieve a zero emission rate associated to their electricity consumption and have a bigger impact on \co emissions in the rest of the system.

\begin{figure*}
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Fraction of hourly demand met with carbon-free electricity.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/used.pdf}
        \label{fig:10-2030-IE-p1-used}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_emisrate.pdf}
        \label{fig:10-2030-IE-p1-ci_emisrate}
    \end{subfigure}

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{\co emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
        \label{fig:10-2030-IE-p1-zone_emissions}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}138
        \caption{Costs of a procurement policy: technological palette~1.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p1-ci_costandrev}
    \end{subfigure}%

    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy: technological palette~2.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p2/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p2-ci_costandrev}
    \end{subfigure}%
    \begin{subfigure}{0.5\textwidth}
        \centering
        \caption{Costs of a procurement policy: technological palette~3.}
        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p3/ci_costandrev.pdf}
        \label{fig:10-2030-IE-p3-ci_costandrev}
    \end{subfigure}

    \caption{Results for the case of Ireland 2030. 10\% participation rate. 
    Data for the Figures \ref{fig:10-2030-IE-p1-used}--\ref{fig:10-2030-IE-p1-zone_emissions} is for the technological palette~1 scenario.}
    \label{fig:10-2030-IE-6plots}
\end{figure*}

@@

result: reducing peaker and flex needs
result: two effects, one stay also in clean grids

plot with e.g. germany system capacity differences
new plot in profile and volume.
